Weak lensing Hierarchy Bayesian Inference

### 2013-02-13 write-up.tex
Update write-up.tex

General relativity predicts that the path of light from a distant
galaxy is distorted by the gravitational potential fluctu- ations
along the line of sight. As dark energy slows the growth of dark matter
structures, these in turn affect the appearance of distant galaxies,
distorting them slightly as gravitational fields deflect their light.
This distortion is known as cosmic shear.()

>>>>

General relativity predicts that the path of light from a distant
galaxy is distorted by the gravitational potential fluctuations
along the line of sight. As dark energy slows the growth of dark matter
structures, these in turn affect the appearance of distant galaxies,
distorting them slightly as gravitational fields deflect their light.
This distortion is known as cosmic shear.()
